*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-21 Code/Manuscript_O2.Rmd
knit to .docx and Html

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: 'Mireille Savoie'
    institute: mta
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    institute: [mtachem, ubc]
  - name: Laurel Genge
    institute: [mta, dfo]
  - name: Julie Nadeau
    institute: mta
  - name: Sylwia Śliwińska-Wilczewska
    institute: [mta, ug]
  - name: Maximilian Berthold
    institute: mta
  - name: Naaman M. Omar
    institute: mta
  - name: Ondřej Prášil
    institute: [mta, algatech]
    main: false
  - name: Amanda M. Cockshutt
    institute: [mtachem, sfx]
    main: false
  - name: Douglas A. Campbell
    institute: mta
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
institute:
  - mta: 'Department of Biology, Mount Allison University, Sackville, New Brunswick, Canada'
  - mtachem: 'Department of Chemistry and Biochemistry, Mount Allison University, Sackville, New Brunswick, Canada'
  - ubc: 'Department of Biology, University of British Columbia, Vancouver, British Columbia, Canada'
  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth, Nova Scotia, Canada'
  - ug: 'Institute of Oceanography, University of Gdansk, Gdynia, Poland'
  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Trebon, Czech Republic'
  - sfx: 'Department of Chemistry, St. Frances Xavier University, Antigonish, Nova Scotia, Canada'
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: FALSE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: 'Mireille Savoie'
    institute: mta
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    institute: [mtachem, ubc]
  - name: Laurel Genge
    institute: [mta, dfo]
  - name: Julie Nadeau
    institute: mta
  - name: Sylwia Śliwińska-Wilczewska
    institute: [mta, ug]
  - name: Maximilian Berthold
    institute: mta
  - name: Naaman M. Omar
    institute: mta
  - name: Ondřej Prášil
    institute: [mta, algatech]
    main: false
  - name: Amanda M. Cockshutt
    institute: [mtachem, sfx]
    main: false
  - name: Douglas A. Campbell
    institute: mta
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
institute:
  - mta: 'Department of Biology, Mount Allison University, Sackville, New Brunswick, Canada'
  - mtachem: 'Department of Chemistry and Biochemistry, Mount Allison University, Sackville, New Brunswick, Canada'
  - ubc: 'Department of Biology, University of British Columbia, Vancouver, British Columbia, Canada'
  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth, Nova Scotia, Canada'
  - ug: 'Institute of Oceanography, University of Gdansk, Gdynia, Poland'
  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Trebon, Czech Republic'
  - sfx: 'Department of Chemistry, St. Frances Xavier University, Antigonish, Nova Scotia, Canada'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: FALSE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
editor_options: 
  markdown: 
    wrap: 72
---
